Rugsafe: A Protocol for Protecting Digital Assets from Rug Pulls

### 2024-08-24 hello_world/rugsafe/paper/paper.tex
updated paper

@@

@@

@@

This burning mechanism enhances the credibility of the user's claim that $C_r$ is a rugged token and provides additional confidence to other participants in the ecosystem.

\subsection{Opportunities for New Developments}
The Rugsafe protocol's structure opens up opportunities for developers to build applications that cater to the needs of rug pull victims. By establishing a market for anticoin tokens $C_a$, new financial products and services can be developed to support users who have suffered losses from rug pulls.

>>>>

%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

This burning mechanism not only signals the user's conviction but also impacts the market by reducing the circulating supply of $C_a$. As $C_a$ tokens are burned, the inverse relationship between the price of $C_a$ and $C_r$ continues to hold, but with a nuanced adjustment reflecting the decreased supply of $C_a$.

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{images/3.png}
\caption{The adjusted inverse logarithmic relationship between the price of the underlying rugged token $C_r$ and the amount of burned anticoins $C_a$. As the price of $C_r$ decreases, the amount of burned $C_a$ decreases, further solidifying the protective mechanism for holders.}
\label{fig:burned_anticoins}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Opportunities for New Ecosystems}
The Rugsafe protocol's structure opens up opportunities for developers to build applications that cater to the needs of rug pull victims. By establishing a market for anticoin tokens $C_a$, new financial products and services can be developed to support users who have suffered losses from rug pulls.

%%%%%%%%%%%%%%%%%%%%%%%%
